Size-environment interaction

### 2021-03-15 analysis/supplementary-materials/size-environment_interaction.Rmd

---
title: "Size-environment interaction"
author: "Eric R. Scott"
date: "2020-01-11"
output: 
  html_notebook: 
    highlight: kate
    theme: yeti
    toc: yes
    toc_float: yes
    number_sections: yes
bibliography: "`r here::here('analysis', 'paper', 'references.bib')`"
---

@@

```{r data, echo=TRUE}
demog <-
  read_csv(
    here("analysis", "data", "derived_data", "ha_survey.csv"),
    col_names = TRUE,
    cols(plot = col_character(),
         bdffp_reserve_no = col_character())
  )
demog <-
  demog %>%
  mutate(log_shts = log(shts + 0.0001),
         log_shts_next = log(shts_next + 0.0001))
```

@@

# Function
Likelihood ratio test for random effects from Tredennick et al.  Tests observed likelihood ratio between model with and without interaction against what would be expected under null.

@@

```{r}
growth_y <- lmer(log_shts_next ~ log_shts + (1|plot) + (1|year), data = demog_post_cf)
growth_sy <- lmer(log_shts_next ~ log_shts + (1|plot) + (log_shts|year), data = demog_post_cf)
AICtab(growth_y, growth_sy)
```

```{r}
lrt_growth <- sy_lrt(growth_y, growth_sy, nsim = 500)
```
Upper = 4.539, observed = 45.689

@@

```{r}
surv_y <- glmer(surv ~ log_shts + (1|plot) + (1|year), family = binomial, data = demog_post_cf)
surv_sy <- glmer(surv ~ log_shts + (1|plot) + (log_shts|year), family = binomial, data = demog_post_cf)
AICtab(surv_y, surv_sy)
```

```{r}
lrt_surv <- sy_lrt(surv_y, surv_sy, nsim = 500)
```
Upper = 3.913, observed = 29.181

@@

```{r}
flwr_y <- glmer(flwr ~ log_shts + (1|plot) + (1|year), family = binomial, data = demog_post_cf)
flwr_sy <- glmer(flwr ~ log_shts + (1|plot) + (log_shts|year), family = binomial, data = demog_post_cf)
AICtab(flwr_y, flwr_sy)
```

```{r}
lrt_flwr <- sy_lrt(flwr_y, flwr_sy, nsim = 500)
```
upper = 4.439, observed = 1.77

@@

```{r}
growth_y_1ha <- lmer(log_shts_next ~ log_shts + (1|plot) + (1|year), data = demog_post_1ha)
growth_sy_1ha <- lmer(log_shts_next ~ log_shts + (1|plot) + (log_shts|year), data = demog_post_1ha)
AICtab(growth_y_1ha, growth_sy_1ha)
```

@@

```{r}
surv_y_1ha <- glmer(surv ~ log_shts + (1|plot) + (1|year), family = binomial, data = demog_post_1ha)
surv_sy_1ha <- glmer(surv ~ log_shts + (1|plot) + (log_shts|year), family = binomial, data = demog_post_1ha)
AICtab(surv_y_1ha, surv_sy_1ha)
```

@@

```{r}
flwr_y_1ha <- glmer(flwr ~ log_shts + (1|plot) + (1|year), family = binomial, data = demog_post_1ha)
flwr_sy_1ha <- glmer(flwr ~ log_shts + (1|plot) + (log_shts|year), family = binomial, data = demog_post_1ha)
AICtab(flwr_y_1ha, flwr_sy_1ha)
```

```{r}

lrt_flwr_1ha <- sy_lrt(flwr_y_1ha, flwr_sy_1ha, nsim = 500)

```

>>>>

---
title: "Size-environment interaction"
author: "Eric R. Scott"
date: "2020-01-11"
output: 
  html_notebook: 
    highlight: kate
    theme: yeti
    toc: yes
    toc_float: yes
    number_sections: yes
bibliography: "`r here::here('analysis', 'paper', 'references.bib')`"
editor_options:
  markdown:
    wrap: sentence
    canonical: true
---

@@

```{r data, echo=TRUE}
demog <-
  read_csv(
    here("analysis", "data", "derived_data", "ha_survey.csv"),
    col_names = TRUE,
    cols(plot = col_character(),
         bdffp_reserve_no = col_character())
  )
# demog <-
#   demog %>%
#   filter(ht_prev < 200, ht < 200) %>% 
#   filter(shts_prev > 0, shts > 0, ht_prev >= 1, ht >= 1) %>% 
#   mutate(size = shts*ht, size_next = shts_next*ht_next, log_size = log(size), log_size_next = log(size_next))
```

@@

# Function

Likelihood ratio test for random effects from Tredennick et al.
Tests observed likelihood ratio between model with and without interaction against what would be expected under null.

@@

```{r}
growth_null <- lmer(log_size_next ~ log_size + (1|plot), data = demog_post_cf)
growth_y <- lmer(log_size_next ~ log_size + (1|plot) + (1|year), data = demog_post_cf)
growth_sy <- lmer(log_size_next ~ log_size + (1|plot) + (log_size|year), data = demog_post_cf)
AICtab(growth_null, growth_y, growth_sy)
```

Significant interaction.

```{r}
#This takes a very long time and gives results qualitatively similar to comparing AIC
lrt_growth <- sy_lrt(growth_y, growth_sy, nsim = 500)
```

@@

```{r}
surv_null <- glmer(surv ~ log_size + (1|plot), family = binomial, data = demog_post_cf)
surv_y <- glmer(surv ~ log_size + (1|plot) + (1|year), family = binomial, data = demog_post_cf)
surv_sy <- glmer(surv ~ log_size + (1|plot) + (log_size|year), family = binomial, data = demog_post_cf)
AICtab(surv_null, surv_y, surv_sy)
```

no interaction

```{r}
lrt_surv <- sy_lrt(surv_y, surv_sy, nsim = 500)
```

@@

```{r}
flwr_null <- glmer(flwr ~ log_size + (1|plot), family = binomial, data = demog_post_cf)
flwr_y <- glmer(flwr ~ log_size + (1|plot) + (1|year), family = binomial, data = demog_post_cf)
flwr_sy <- glmer(flwr ~ log_size + (1|plot) + (log_size|year), family = binomial, data = demog_post_cf)
AICtab(flwr_null, flwr_y, flwr_sy)
```

No interaction

```{r}
lrt_flwr <- sy_lrt(flwr_y, flwr_sy, nsim = 500)
```

@@

```{r}
growth_null_1ha <- lmer(log_size_next ~ log_size + (1|plot), data = demog_post_1ha)
growth_y_1ha <- lmer(log_size_next ~ log_size + (1|plot) + (1|year), data = demog_post_1ha)
growth_sy_1ha <- lmer(log_size_next ~ log_size + (1|plot) + (log_size|year), data = demog_post_1ha)
AICtab(growth_null_1ha, growth_y_1ha, growth_sy_1ha)
```

significant interaction

@@

```{r}
surv_null_1ha <- glmer(surv ~ log_size + (1|plot), family = binomial, data = demog_post_1ha)
surv_y_1ha <- glmer(surv ~ log_size + (1|plot) + (1|year), family = binomial, data = demog_post_1ha)
surv_sy_1ha <- glmer(surv ~ log_size + (1|plot) + (log_size|year), family = binomial, data = demog_post_1ha)
AICtab(surv_null_1ha, surv_y_1ha, surv_sy_1ha)
```

No interaction or effect of year.

@@

```{r}
flwr_null_1ha <- glmer(flwr ~ log_size + (1|plot), family = binomial, data = demog_post_1ha)
flwr_y_1ha <- glmer(flwr ~ log_size + (1|plot) + (1|year), family = binomial, data = demog_post_1ha)
flwr_sy_1ha <- glmer(flwr ~ log_size + (1|plot) + (log_size|year), family = binomial, data = demog_post_1ha)
AICtab(flwr_null_1ha, flwr_y_1ha, flwr_sy_1ha)
``

significant interaction?

lrt_flwr_1ha <- sy_lrt(flwr_y_1ha, flwr_sy_1ha, nsim = 500)
```
